Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2020-08-10 FDT2020/Introduction.tex
A contribution summary list

\cindy{We probably need an explicit list of contributions.  It could be another subsection of the introduction.  This will help the reviewer and eventually, if published, the reader.}

>>>>

\cindy{We probably need an explicit list of contributions.  It could be another subsection of the introduction.  This will help the reviewer and eventually, if published, the reader.}
\subsection{Contribution summary}
In summary, this papers's contributions are:
\begin{itemize}
\item We give an algorithm to express any feasible point for the LP relaxation of a binary IP (or a \{0,1,2\} IP) as a convex combination of feasible solutions, provided the IP integrality gap is bounded.  This is the Fractional Decomposition Tree (FDT) algorithm.
\item We give a simpler, faster algorithm algorithm to give one feasible solution for any IP with bounded integrality gap. If this algorithm fails, then the integrality gap is infinite.
\item We experimentally show that FDT can give good approximate solutions to small instances of vertex-cover and tree-augmentation problems.
\item We show that the integrality gap for 2EC (minimum 2-edge-connected sub-multigraph) is at most $\frac{6}{5}$ for Carr-Vempala points with at most $12$ vertices on the cycle formed by the fractional edges, matching the lower bound for integrality gap for 2EC for these instances.
\item We demonstrate (with tree augmentation and 2EC) how FDT exeriments can support theoretical work on integrality gaps for specific problems.
\end{itemize}
